### 2016-08-04 architecture.tex
Add a note about dotprint
I hope, this addresses 3rd point of the
reviewer 2 (Lines 151-153).

A useful way to view an expression tree is using the \texttt{srepr} function, which
returns a string representation of an expression as valid Python code
with all the nested class constructor calls to create the given expression.
\begin{verbatim}
>>> srepr(expr)
"Add(Mul(Symbol('x'), Symbol('y')), Integer(2))"
\end{verbatim}

>>>>

A useful way to view an expression tree is using the \texttt{srepr} function, which
returns a string representation of an expression as valid Python code\footnote{
The \texttt{dotprint} function from the \texttt{sympy.printing.dot} package
prints output to dot format, which can be rendered with Graphviz to
visualize expression trees graphically.}
with all the nested class constructor calls to create the given expression.
\begin{verbatim}
>>> srepr(expr)
"Add(Mul(Symbol('x'), Symbol('y')), Integer(2))"
\end{verbatim}
